My English activity log

### 2019-12-08 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 08/12 + test % logo

>>>>

03/12/2019 : I watched a video about microscopes https://www.youtube.com/watch?v=tVcEEw6qbBQ.

05/12/2019 : I watched a video about reproductive adaptations https://www.youtube.com/watch?v=b_w4Nexv-0s.

07/12/2019 : I watched a video about DNA replication https://www.youtube.com/watch?v=Qqe4thU-os8.

08/12/2019 : I watched a video about imprinting https://www.youtube.com/watch?v=vwaiVxxpi7E and I read the eleventh chapter of "The Hobbit".
